Explore anomalies

### 2017-11-21 analysis/evi/explore_anomalies.Rmd
remove errors // add percentage browing

plot_a_pop
pdf(file=paste0(di, "/out/anomalies/plot_anoma_EVI_pop_a.pdf"), height = 14, width = 14)
plot_a_pop
dev.off()
```

@@

plot_nora_pop 
pdf(file=paste0(di, "/out/anomalies/plot_anoma_EVI_pop_nora.pdf"), height = 14, width = 14)
plot_nora_pop 
dev.off()
```

@@

plot_sa_pop
pdf(file=paste0(di, "/out/anomalies/plot_anoma_EVI_pop_sa.pdf"), height = 14, width = 14)
plot_sa_pop
dev.off()
```

@@

>>>>

plot_a_pop
pdf(file=paste0(di, "/out/anomalies/evi/plot_anoma_EVI_pop_a.pdf"), height = 14, width = 14)
plot_a_pop
dev.off()
```

@@

plot_nora_pop 
pdf(file=paste0(di, "/out/anomalies/evi/plot_anoma_EVI_pop_nora.pdf"), height = 14, width = 14)
plot_nora_pop 
dev.off()
```

@@

plot_sa_pop
pdf(file=paste0(di, "/out/anomalies/evi/plot_anoma_EVI_pop_sa.pdf"), height = 14, width = 14)
plot_sa_pop
dev.off()
```

@@

## Analisis espacial bronwing vs. greenning

```{r}
sa2005 <- anomalias_evimean %>% filter(y == 2005) %>% 
  mutate(type = ifelse(sa < -1, "browning", 
                       ifelse(sa > 1, "greening", "no change"))) %>% 
  group_by(clu_pop2, type) %>% 
  dplyr::summarise(count_clu = n()) %>% 
  group_by(clu_pop2) %>% 
  mutate(per = round(count_clu / sum(count_clu)*100, 2),
         y = 2005)

sa2012 <- anomalias_evimean %>% filter(y == 2012) %>% 
  mutate(type = ifelse(sa < -1, "browning", 
                       ifelse(sa > 1, "greening", "no change"))) %>% 
  group_by(clu_pop2, type) %>% 
  dplyr::summarise(count_clu = n()) %>% 
  group_by(clu_pop2) %>% 
  mutate(per = round(count_clu / sum(count_clu)*100, 2),
         y = 2012)

per_sa <- sa2005 %>% rbind(sa2012) %>% as.data.frame()

per_sa %>% kable()

write.csv(per_sa, file=paste0(di, '/out/anomalies/evi/percen_browing_greening.csv'), row.names = F)

```{r per_evi_browing_greening}
# How many pixels 
npixels <- length(unique(anomalias_evimean$iv_malla_modi_id))
# 912

saper <- anomalias_evimean %>% filter(y %in% c(2005, 2012))

saper %>% ggplot(aes(sa)) + facet_grid(y~clu_pop2) + geom_histogram()
